---
title: "InfoVis Final Project Data Exploration • Plastic Pollution"
author: "Kylie Lin, Sherry Xue, Annika Nerella, Nawar Alhaddad, Mackenzie Wood"
output:
  pdf_document:
    toc: yes
always_allow_html: true
---

## Introduction

```{r, include=F, warning=F, message=F}
# data wrangling
library(tidyverse)
library(janitor)
library(naniar)
library(skimr)

# visualizing
library(ggdist)
library(DT)
library(patchwork)

```


```{r, include=F, message=F, warning=F}
# hello! code goes here
# this doc is combining everything
sector_polymer <- read_csv("data/plastic-production-by-sector.csv") %>% 
  clean_names()
plastics_time <- read_csv("data/global-plastics-production.csv") %>% 
  clean_names()
microp_ocean <- read_csv("data/microplastics-in-ocean.csv") %>% 
  clean_names()
macrop_ocean <- read_csv("data/macroplastics-in-ocean.csv") %>% 
  clean_names()

```

Our Final Project is guided by four questions: Where does polluting plastic come from? How much polluting plastic is there in the world and how much has there been over time? Where does the plastic end up eventually? Why should I care; i.e. where does the plastic go in my life? Each of the explored datasets below answers one of these guiding questions (two datasets are used to answer where plastic goes).

## Plastics by Industrial Sector + Polymer Types

```{r, echo=FALSE}
sector_polymer %>% 
  select(-code) %>% 
  datatable()
```


```{r, echo=T, results='hide'}
skim_without_charts(sector_polymer)
```


```{r, echo=FALSE}
tibble(
  Missingness = "No Missingness",
  `Industry/Polymer Type Count` = 19,
  Year = "Only 2015",
 `Production Range` = str_c(min(sector_polymer$primary_plastic_production_million_tonnes), " to ", max(sector_polymer$primary_plastic_production_million_tonnes))
) %>% 
  datatable()
```


## Production Over Time

```{r, echo=F}
plastics_time %>%
  select(-code) %>% 
  rename("Production (tonnes)" = global_plastics_production_million_tonnes) %>%
  datatable()

```

```{r, echo=T, results='hide'}
skim_without_charts(plastics_time)
```


```{r, echo=FALSE}
tibble(
  Missingness = "No Missingness",
  `Year Range` = str_c(min(plastics_time$year), " to ", max(plastics_time$year)),
  `Number of Years` = 66,
  `Plastics Range` = str_c(min(plastics_time$global_plastics_production_million_tonnes), " to ", max(plastics_time$global_plastics_production_million_tonnes)),
) %>% 
  datatable()
```

## Micro and Macro Plastic Pollution in the Ocean

### Macro Plastics

```{r}

```

### Micro Plastics

```{r, echo=FALSE}
tibble(
   Missingness = "No Missingness",
  `Number of Observations` = 303,
  Year = str_c(min(microp_ocean$year), " to ", max(microp_ocean$year)),
 `Plastic Count Range` = str_c(0, " to ", 2652700)
) %>% 
  datatable()

```


